\begin{thebibliography}{99}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%ICP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{kje1} KJER, H., WILM, J.
Evaluation of surface registration algorithms for PET motion correction.
\textit{In Bachelor thesis,}
Technical University of Denmark, Informatics and
Mathematical Modeling, Denmark, 2010.

\bibitem{besl1} BESL, P., MCKAY, N.
A Method for Registration of 3-D Shapes. 
\textit{IEEE Trans. on
Pattern Analysis and Machine Intelligence (Los Alamitos, CA, USA: IEEE Computer Society),}
Vol.17, No.8, pp. 239-256, 1992

\bibitem{che1} CHEN, Y., MEDIONI G.
Object modelling by registration of multiple range images. Image Vision Comput. 
\textit{Newton, MA, USA: Butterworth-Heinemann,}
145–155. doi:10.1016/0262-8856(92)90066-C.

\bibitem{kje2} KJER, H., WILM, J.
Evaluation of surface registration algorithms for PET motion correction.
\textit{Bachelor thesis, }
Technical University of Denmark, Informatics and
Mathematical Modeling, Denmark, 2010.

\bibitem{kon1} KONEČNÝ, J.
Principles of mobile service robots.
\textit{Dissertation thesis,}
Vysoká škola báňská - Technická univerzita Ostrava (2014).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Monte Carlo
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibitem{fox1} FOX, D., WOLFRAM, B., DELLAERT, F., THURN, S.
Monte Carlo Localization: Efficient Position Estimation for Mobile Robots.
\textit{In Proceedings of the Sixteenth National,}
Conference on Artificial Intelligence. Orlando, USA, 1999.

\bibitem{fox2} FOX, D., WOLFRAM, B., DELLAERT, F., THURN, S.
Robust Monte Carlo Localization for Mobile Robots.
Computer Science Department. University of Freiburg, Germany, 2001.

\bibitem{che2} CHEEIN, F., TOIBERO, J., DI SCIASCIO, F., CARELLI, R., LOBO PEREIRA, F.
Monte carlo uncertainty maps-based for mobile robot autonomous slam navigation. 
\textit{In Industrial Technology (ICIT),}
2010 IEEE International Conference on, pp. 1433–1438 (2010).

\bibitem{thr1} THRUN S., BURGARD W., FOX D.
Probalistic Robotics.
\textit{MIT Press,}
2005. Ch. 8.3 ISBN 9780262201629.

\bibitem{ant1} ANTECKÝ, J.
Aplikace metody zarovnání snímku pro lokalizaci autonomního robotu.
\textit{Master’s thesis,}
Vysoká škola bánská - Technická univerzita Ostrava (2014).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%APR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibitem{web1} WEBER, J., JÖRG, K., PUTTKAMER, E.
APR - Global scan matcing using anchor point relationships.
\textit{In Proc. of the 6th international conference on intelligent autonomous systems,} IOS press, pp. 471-478, 2000.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%histogrsm
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{qui1} QUI, Q., HAN, J.
Laser Scan Matching Using Multiplex Histograms with Feature Components.
\textit{In Proc.Int. Conf. on Robotics and Biometics,} Guilin, China, December 19-23. 2009.

%%Korelace
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{zva1} ZVÁROVÁ J.
Biomedicínská statistika I. : Základy statistiky pro biomedicínské obory
\textit{Dotisk 1. vydání Praha : Karolinum, 1998. 218 s. ISBN 80-7184-786-0.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Afinní transformace
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{ols1} OLŠÁK, P.
Afinní transformace [online]
\textit{2013 [cit. 2015-09-13]. Dostupné: http://petr.olsak.net/bilin/afinita-v2.pdf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Weiler atherton
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{wei1} WEILER, K., Atherton, P.
Hidden Surface Removal using Polygon Area Sorting
\textit{Computer Graphics, 11(2):214-222, 1977.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%LMS SICK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{sic1} SICK AG.
LMS SICK 100: Laserový senzor [online]. [cit. 2015-09-26]. Dostupné z: 
\textit{https://www.sick.com/de/en/detection-and-ranging-solutions/2d-laser-scanners/lms1xx/lms100-10000/p/p109841}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%Laser sensor
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{don1} DONG-GI W., JONG-KYU O., CHAN-HO L., SANG-HUN L., SUNG-HYUN J.
Development of a multi-line laser sensor based robotic 3D measurement system
\textit{Control, Automation and Systems (ICCAS), 2011 11th International Conference on, 2093-7121, 2011.}

\bibitem{kov1} KOVACS, E. a A.S.V. MS.,
Laser sensor based measurement system with 2D motion control.
\textit{International Symposium on Power Electronics, Electrical Drives, Automation and Motion, 2006. SPEEDAM 2006 [online]. 2006 [cit. 2015-09-26]. DOI: 10.1109/speedam.2006.1649854.}

\bibitem{sai1} SAITO R., WATANABE K., NAGAI I.,
Laser odometry taking account of the tilt on the laser sensor. In: 
\textit{2015 10th Asian Control Conference (ASCC) [online]. 2015 [cit. 2015-09-26]. DOI: 10.1109/ascc.2015.7244648.}

\bibitem{sic2} SICK AG.
Sensors for the detection of transparent objects.
\textit{Sensors for the detection of transparent objects [online]. [cit. 2015-10-03]. Dostupné z: https://www.sick.com/media/pdf/2/72/772/IM0047772.PDF}

\bibitem{sic3} SICK AG.
LMS SICK 100: Laserový senzor [online]. [cit. 2015-09-26]. Dostupné z: 
\textit{http://www.hizook.com/files/publications/SICK\_
\hspace{-0.8mm}LMS100.pdf}

\myparagraph{Citace obrázků}

\bibitem{pic1}
Iterative Closest Point Algorithm [online]. F. Colas, 2011 [cit. 2015-11-30]. Dostupné z: \textit{http://www.asl.ethz.ch/education/master/info-process-rob/ICP.pdf}

\bibitem{pic2}
WEBER, Joachim, Klaus-Werner JÖRG a Ewald von PUTTKAMER. APR - Global scan matcing using anchor point relationships [online]. [cit. 2015-11-30]. DOI: 10.1.1.114.3843. Dostupné z: \textit{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.114.3843}


\bibitem{pic3} ANTECKÝ, J.
Aplikace metody zarovnání snímku pro lokalizaci autonomního robotu.
\textit{Master’s thesis,}
Vysoká škola bánská - Technická univerzita Ostrava (2014).

\bibitem{pic4} KONEČNÝ, J.
Principles of mobile service robots.
\textit{Dissertation thesis,}
Vysoká škola báňská - Technická univerzita Ostrava (2014).

\bibitem{pic5} SICK AG.
LMS SICK 100: Laserový senzor [online]. [cit. 2015-09-26]. Dostupné z: 
\textit{http://www.hizook.com/files/publications/SICK\_
\hspace{-0.8mm}LMS100.pdf}

\bibitem{mf1}
Principy programování: Robustnost a korektnost. Zive.cz [online]. Praha: Mladá fronta a.s., 2009 [cit. 2016-01-16]. Dostupné z: \textit{http://principyprogramovani.blog.zive.cz/2009/09/robustnost-a-korektnost/}


\end{thebibliography}